Analysis of nested multilevel Monte Carlo \\ using approximate Normal random variables

### 2021-02-16 paper.tex
Minor sentence alteration.

The three approximations are all motivated by the different hardware features 
of modern CPUs and GPUs (manycore graphics processing units). The 
implementation details and the resulting execution performance of 
the three approximations are explained more fully in \cite{sheridanmethven2020approximating,sheridan-methven2020thesis}.

@@

\begin{figure}
\begin{center}
\subfloat[Quantised approximation]{\includegraphics[width = 4.5in]{figs/fig1a}} \\
\subfloat[Piecewise linear approximation on dyadic intervals]{\includegraphics[width = 4.5in]{figs/fig1b}} \\
\subfloat[Polynomial approximation]{\includegraphics[width = 4.5in]{figs/fig1c}}
\end{center}
\caption{Three approximations of the inverse Normal CDF.}
\label{fig:fig1}
\end{figure}

@@

\begin{figure}[tb]
\centering
%\includegraphics[width=\linewidth]{figs/numeric_results_different_approximations}
\includegraphics[width=0.7\linewidth]{figs/fig2}
\caption{MLMC variances for two different output functions, with
  reference lines proportional to $2^{-2\ell}$ and $2^{-\ell}$.}
\label{fig:numeric_results}
\end{figure}

>>>>

The three approximations are all motivated by the different hardware features 
of modern CPUs and GPUs (manycore graphics processing units). Their analysis, 
implementation details, and resulting execution performance are explained more fully in \cite{sheridanmethven2020approximating,sheridan-methven2020thesis}.

@@

\begin{figure}
\begin{center}
\subfloat[Quantised approximation]{\includegraphics[width = 4.5in]{fig1a}} \\
\subfloat[Piecewise linear approximation on dyadic intervals]{\includegraphics[width = 4.5in]{fig1b}} \\
\subfloat[Polynomial approximation]{\includegraphics[width = 4.5in]{fig1c}}
\end{center}
\caption{Three approximations of the inverse Normal CDF.}
\label{fig:fig1}
\end{figure}

@@

\begin{figure}[tb]
\centering
%\includegraphics[width=\linewidth]{figs/numeric_results_different_approximations}
\includegraphics[width=0.7\linewidth]{fig2}
\caption{MLMC variances for two different output functions, with
  reference lines proportional to $2^{-2\ell}$ and $2^{-\ell}$.}
\label{fig:numeric_results}
\end{figure}
